---
title: "In-process assessment of ITN campaign household registration interim report" 
subtitle: "\n &nbsp;  \n  Country and/or location of mass distribution campaign:   \n  Intended date of campaign:  \n  Date(s) of household registration:  \n &nbsp;"
author: "Author(s): FirstName LastName"
date: "Report date:`r format(Sys.time(), '%d %B, %Y')`"
output: 
  word_document:
    reference_docx: ref-doc.docx

---

```{r setup, include = FALSE}

# Libraries
library(readxl)
library(tidyverse)
library(flextable)
library(officer)
library(purrr)
library(knitr)
library(janitor)
library(openxlsx)

# Visual themes

# flextable theme
my_theme <- function(x, ...) {
    x <- set_table_properties(x, layout = "fixed")
    x <- border_remove(x)
    std_border <- fp_border(width = 1, color = "darkgray")
    x <- border_outer(x, part="all", border = std_border )
    x <- border_inner_h(x, border = std_border, part="all")
    x <- border_inner_v(x, border = std_border, part="all")
    x <- fontsize(x, size = 8, part = "body")
    x <- fontsize(x, size = 9, part="header")
    x <- fontsize(x, size = 7, part="footer")
    x <- set_table_properties(x, layout = "autofit")
    x <- bold(x, part = "header")
    x <- align(x, i = 1, j = NULL, align = "left", part = "header")
    x <- set_table_properties(x, layout = "autofit", width = 1)
    x
}

# Set knitr options
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      ft.align = "left",
                      fig.width = 6.5,
                      fig.height = 4,
                      dpi = 300) 

```


```{r import, include = FALSE}
source("1 In-process check and clean.R") # This generates the data frames that are used for this report. It also exports clean, raw data into a subfolder.
# You can also import from the clean, raw data subfolder (in which case you will need to export the data daily)

#- Set the reporting day
# This is the day that will be used when reporting daily results; update it daily to use the most recent sampling day
day = 3

# For the purposes of demonstrating the code, filter data up to day three to simulate running this report part way through fieldwork
# If you are running this report daily, then you do not need to filter and can remove or comment out this line
hh <- hh %>% filter(survey_day <= 3)

```

&nbsp; <!-- This add line break between the title section and start of main text -->

This is an adaptable template that provides guidance and content examples for daily reporting on an in-process assessment of household registration ahead of an ITN distribution campaign, following the Alliance for Malaria Prevention (AMP) recommendations. 

The report is intended to be generated daily and shared with HHR programme staff, along with national malaria programme staff, and partners leading and supporting an in-process campaign assessment. HHR programme staff should review the level and reasons for errors occurring during HHR, and provide feedback based on results to individual HHR teams in the morning of each new HHR day. 

The starting point for this R Markdown is a cleaned data set generated by running the R script: *1 In-process check and clean.R*. The output of the R Markdown is a series of graphs and tables, summarizing the results of the in-process HHR assessment. 

**The components of this output are**:

- Table 1. Completeness and HHR error by district
- Table 2. Daily error and error reason list
- Table 3. Percentage of households with HHR errors by assessment day
- Figure 1. Households with registration errors by assessment day 
- Table 4. Percentage of households with HHR errors by district for each region, daily and cumulative total
- Table 5. Percentage of households with HHR errors by region, daily and cumulative total
- Figure 2. Reasons for household error by region
- Table 7a. Distribution of HHR error reasons by district for a given region, daily
- Table 7b. Distribution of HHR error reasons by district for a given region, cumulative
- Table 8a. Distribution of HHR error by reasons by region, daily
- Table 8b. Distribution of HHR error by reason by region, cumulative
- Table  9. Campaign assessment summary of total HHR errors and direction of error
- Table 10. Campaign summary of assessment outcomes and categorized reasons for errors
- Table 11. Classification of lots based on correct count of eligible persons during HHR.

## These are results from Day `r day`
Programme staff should review the frequency of and reasons for errors occurring during the previous day's household registration activities. These are given in Table 1 and 2. After reviewing these results, programme staff should provide feedback to individual HHR teams in the morning of each new work day.

## Errors and completeness by district (lot)
Table 1 summarizes the number of households that were not registered and number of households with an error in the count of eligible persons in the household during registration. Each district (lot) must have 60 interviews to be considered as completed. The shading of the table is according to region. 

```{r table1}
#- Create a table with the number of HH interviewed by district and number of HHs with errors in count of eligible people
t_1 <- hh %>% filter(survey_day == day) %>%
  group_by(region, district) %>%
  summarise(across(c(interviewed, hhr_err, novisit, hhr_err_ct), \(x) sum(x, na.rm = TRUE)), .groups = "drop") %>%
  mutate(lot_done = case_when(interviewed == 60 ~ "Yes",
                              interviewed < 60 ~ "No")) %>%
  select(region, district, interviewed, lot_done, hhr_err, novisit, hhr_err_ct)

#- Add all planned sampling locations 
# If you want to insert all of the planned sampling locations, including those without any data yet, you can pull all the levels from the pop.data file and merge with the table here
#locations <- pop.data %>% select(region, district)
#t_1 <- left_join(locations, t_1, by = c("region", "district")) 

# Fill in 0/incomplete
#t_1 <- t_1 %>% mutate(interviewed = replace_na(interviewed, 0),
#                        lot_done = case_when(interviewed > 9 ~ "Yes",
#                              interviewed < 10 ~ "No"),
#                        novisit = case_when(interviewed == 0 ~ "-",
#                                            TRUE ~ as.character(novisit)),
#                        hhr_err = case_when(interviewed == 0 ~ "-",
#                                            TRUE ~ as.character(hhr_err)))

# Create a flextable object
t_1 %>%
  flextable() %>%
  # Create grouping by region
  merge_v(j = "region") %>%
  valign(j = "region", valign = "top") %>%
  bg(i = ~ region == 1, bg = "#f2f2f2", part = "body") %>% # This colors the rows by region 
  bg(i = ~ region == 2, bg = "#e6f7ff", part = "body") %>%
  bg(i = ~ region == 3, bg = "#fff2e6", part = "body") %>%
  # Set header and caption
  set_header_labels(region = "Region",
                    district = "District",
                    interviewed = "HHs with data",
                    lot_done = "Lot complete",
                    hhr_err = "HHs with any errors",
                    novisit = "HHs that reported no visit by HHR team",
                    hhr_err_ct = "HHs with mismatch in eligible persons count") %>%
  set_caption(caption = paste("Table 1. Completeness and HHR errors by district: ", 
                              paste("Assessment day ", day)),
              style = "Table Caption") %>% 
  my_theme()

```

Table 2 lists the daily HHR errors by cluster and household ID, including unregistered households and mismatches in household counts. The error reason category is presented and where the assessor noted further details on the reason for the mismatch, they are provided. An Excel file is also exported with the file name "details of daily errors_day`r day`.xlsx" that includes any further details on the reason for the mismatch. 

```{r table2}

# Create table with the daily mismatches between HHR and assessment
t_2 <- hh %>% filter(hhr_err == 1 & survey_day == day) %>%
  mutate(reason_mismatch = case_when(novisit == 1 ~ "HH not registered",
                                     reason_mismatch == 1 ~ "HHR counted ineligible person(s) as eligible",
                                     reason_mismatch == 2 ~ "HHR counted eligible person(s) as ineligible",
                                     reason_mismatch == 3 ~ "HHR did not follow HH definition",
                                     reason_mismatch == 4 ~ "Household likely inflated number of eligible persons",
                                     reason_mismatch == 5 ~ "HHR miscount, reason unknown",
                                     reason_mismatch == 96 ~ "Other reason"), #!!! Categories in dummy tables don't match reasons in ODK form
         hhr_count = case_when(novisit == 1 ~ "-",
                               TRUE ~ as.character(hhr_count))) %>%
  select(district, cluster, hhid, hh_n, hhr_count, survey_count, reason_mismatch, descr_mismatch)
  
# Export an Excel version of all the households with errors to be used for review and corrective action as needed
t_2_exp <- t_2 %>%
  rename("Elig persons HHR" =  hhr_count,
         "Elig persons assessment" = survey_count,
         "Reason for error" = reason_mismatch,
         "Details of mismatch" = descr_mismatch)

write.xlsx(t_2_exp, paste0("details of daily errors_day", day, ".xlsx"))

# Create a flextable object
t_2 %>% 
  select(-descr_mismatch) %>%
  flextable() %>% 
  set_header_labels(district = "District",
                    cluster = "Cluster number within district",
                    hh_n = "HH number within cluster", 
                    hhid = "HH ID",
                    hhr_count = "Eligible persons: HHR",
                    survey_count = "Eligible persons: assessment",
                    reason_mismatch = "Reason (category)") %>%
  # Formatting
  colformat_double(j = c("cluster", "hhid"), big.mark = "", decimal.mark = ".", digits = 0) %>%
  my_theme() %>%
  set_caption(caption = paste("Table 2. Daily error and error reason line list: ", 
                              paste("Assessment day ", day)),
              style = "Table Caption")

```

## Error trends over time
The number and percentage of households with errors for each survey day is given in the following table and bar chart. Both the daily and cumulative numbers are provided to show trends in errors over time. 

```{r tablea3}
t_3 <- hh %>% group_by(survey_day) %>%
  summarise(across(c(interviewed, hhr_err), \(x) sum(x, na.rm = TRUE)), .groups = "drop") %>%
  mutate(perc_err = round(hhr_err/interviewed*100, 0))

# Create a flextable object
flextable(t_3) %>% 
  # Set header
  colformat_num(j = "perc_err", suffix = "%", digit = 1) %>%
  set_header_labels(survey_day = "Day",
                    interviewed = "HHs with data",
                    hhr_err = "HHs with errors",
                    perc_err = "Percentage of HHs with errors") %>%
  # Set footer
    add_footer_lines(paste("Lot definition: district\n",
                           "Target number of lots in assessment: 50\n", 
                           "Assessment design: 10 HHs per lot per day\n",
                           "Source of data: Assessment recount vs participant recall of HHR\n",
                           "Percentage values are based on unweighted counts")) %>%
  # Set caption
  set_caption(caption = "Table 3. Percentage of households with HHR errors, by assessment day", 
              style = "Table Caption") %>% 
  my_theme()

```

The following bar chart shows the number (left axis) and percentage (right axis) of households with errors, by assessment day.

```{r figurea3}
# Plot of number and percentage of households with registration errors, by assessment day
t_3 %>% 
  ggplot() +
  geom_bar(aes(x = survey_day, hhr_err, fill = "Number of HHs with errors"), stat = "identity") +
  geom_text(aes(x = survey_day, hhr_err, label=hhr_err), vjust = -0.6, size = 3.5) +
  geom_line(aes(x = survey_day, y = perc_err, color = "Percentage of HHs with errors"), linewidth = 1.8) + # Note: if the number of HH with errors is very different than the percentage of errors (e.g. 45 households but that is 5% of the total sample) then you may need to transform perc_err by multiplying by an appropriate coefficient
  scale_y_continuous(limits = c(0, 55), breaks = c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55), name = "Number of households", 
                     sec.axis = sec_axis(~./100, breaks = c(0, 0.05, 0.10, 0.15, 0.20, 0.25, 0.30, 0.35, 0.40, 0.45, 0.50, 0.55), labels = scales::label_percent(), name = "Percentage of households")) + # !!! Limits and breaks need to be manually updated based on the number of errors
  labs(title = "Households with registration errors, by assessment day", x = "Assessment day") +
  scale_fill_manual(name = NULL, values = c("Number of HHs with errors" = "#156082")) +
  scale_color_manual(name = NULL, values = c("Percentage of HHs with errors" = "#E97132")) +
  theme_minimal() +
  theme(legend.position = "bottom") +
  guides(fill = guide_legend(order = 1), 
         colour = guide_legend(order = 2))
  
```

The number of households with errors by district (lot) for each region is summarized below in Table 4. 

```{r tablea4}

# Daily and cumulative errors by district (lot)

# Create a table with the daily results
t_4a <- hh %>% group_by(region, district, survey_day) %>%
  summarise(across(c(interviewed, hhr_err_ct), \(x) sum(x, na.rm = TRUE)), .groups = "drop") %>%
  mutate(perc_err = round(hhr_err_ct/interviewed*100, 0)) %>%
  select(region, district, survey_day, interviewed, hhr_err_ct, perc_err)

# Create a table with the cumulative results
t_4b <- hh %>% filter(survey_day <= day) %>%
  group_by(region, district) %>%
  summarise(across(c(interviewed, hhr_err_ct), \(x) sum(x, na.rm = TRUE)), .groups = "drop") %>%
  mutate(perc_err = round(hhr_err_ct/interviewed*100, 0)) %>%
  select(region, district, interviewed, hhr_err_ct, perc_err) %>%
  rename(interviewed_cumu = interviewed,
         hhr_errcumu = hhr_err_ct,
         perc_errcumu = perc_err)

# Join cumulative results to daily results by region and district
t_4 <- left_join(t_4a, t_4b, by = c("region", "district"))

# Filter by day
t_4 <- t_4 %>% filter(survey_day == day) %>%
  select(region, district, interviewed, hhr_err_ct, perc_err, interviewed_cumu, hhr_errcumu, perc_errcumu)

# Create a totals row
t_4tot <- t_4 %>% summarise(region = "",
                              district = "Total",
                              interviewed = sum(interviewed, na.rm = TRUE),
                              hhr_err_ct = sum(hhr_err_ct, na.rm = TRUE),
                              perc_err = 0,
                              interviewed_cumu = sum(interviewed_cumu, na.rm = TRUE),
                              hhr_errcumu = sum(hhr_errcumu, na.rm = TRUE),
                              perc_errcumu = 0) %>%
  mutate(perc_err = round(hhr_err_ct/interviewed*100, 0),
         perc_errcumu = round(hhr_errcumu/interviewed_cumu*100, 0))

# Add totals to tibble
t_4 <- rbind(t_4, t_4tot)

# Create a flextable object
t_4 %>% mutate(spacer = "") %>% # add a spacer for flextable
  select(region, district, interviewed, hhr_err_ct, perc_err, spacer, interviewed_cumu, hhr_errcumu, perc_errcumu) %>%
  flextable() %>%
  # Create grouping by region
  merge_v(j = "region") %>%
  valign(j = "region", valign = "top") %>%
  bg(i = ~ region == 1, bg = "#f2f2f2", part = "body") %>% # This colors the rows by region 
  bg(i = ~ region == 2, bg = "#e6f7ff", part = "body") %>%
  bg(i = ~ region == 3, bg = "#fff2e6", part = "body") %>%
  # Set headers
  set_header_labels(region = "Region",
                    district = "District",
                    interviewed = "HHs with data",
                    hhr_err_ct = "Number of HHs",
                    perc_err = "Percentage of HH",
                    spacer = "",
                    interviewed_cumu = "HHs with data",
                    hhr_errcumu = "Number of HHs",
                    perc_errcumu = "Percentage of HH") %>%
  add_header_row(values = c("", "Incorrect count of eligible persons at HHR", "", "Incorrect count of eligible persons at HHR" ), colwidths = c(2, 3, 1, 3)) %>%
  add_header_row( values = c("", "Daily results", "", "Cumulative results"), colwidths = c(2, 3, 1, 3)) %>%
  # Footer
  add_footer_lines(paste("Lot definition: district\n",
                         "Source of data: Assessment recount vs participant recall of HHR\n",
                         "Percentage values are based on unweighted counts")) %>%
  # Formatting
  colformat_num(j = "perc_err", suffix = "%") %>%
  colformat_num(j = "perc_errcumu", suffix = "%") %>%
  align(j = "region", align = "left", part = "body") %>%
  align(i = 2, j = NULL, align = "left", part = "header") %>%
  align(i = 3, j = NULL, align = "left", part = "header") %>%
  # Shade the spacer column as the visual break 
  bg(j = "spacer", bg = "#E6E6E6", part = "all") %>%
  width(j = "spacer", width = 0.1) %>%
  my_theme() %>%
  # Set header
  set_caption(caption = paste("Table 4. Percentage of households with HHR errors by district for a given region, daily and cumulative total: ",
                              paste("Assessment day ", day)), 
              style = "Table Caption")

```

Table 5 presents the same data at Table 4 but summarized by region rather than district (lot). 

```{r tablea5, echo = FALSE}

# Create a table with the daily results
t_5a <- hh %>% group_by(region, survey_day) %>%
  summarise(across(c(interviewed, hhr_err_ct), \(x) sum(x, na.rm = TRUE)), .groups = "drop") %>%
  mutate(perc_err = round(hhr_err_ct/interviewed*100, 0)) %>%
  select(region, survey_day, interviewed, hhr_err_ct, perc_err)

# Create a table with the cumulative results
t_5b <- hh %>% filter(survey_day <= day) %>%
  group_by(region) %>%
  summarise(across(c(interviewed, hhr_err_ct), \(x) sum(x, na.rm = TRUE)), .groups = "drop") %>%
  mutate(perc_err = round(hhr_err_ct/interviewed*100, 0)) %>%
  select(region, interviewed, hhr_err_ct, perc_err) %>%
  rename(interviewed_cumu = interviewed,
         hhr_errcumu = hhr_err_ct,
         perc_errcumu = perc_err)

# Join cumulative results to daily results by region and district
t_5 <- left_join(t_5a, t_5b, by = "region")

# Filter by day
t_5 <- t_5 %>% filter(survey_day == day) %>%
  select(region, interviewed, hhr_err_ct, perc_err, interviewed_cumu, hhr_errcumu, perc_errcumu)

# Create a totals row
t_5tot <- t_5 %>% summarise(region = "Total",
                              interviewed = sum(interviewed, na.rm = TRUE),
                              hhr_err_ct = sum(hhr_err_ct, na.rm = TRUE),
                              perc_err = 0,
                              interviewed_cumu = sum(interviewed_cumu, na.rm = TRUE),
                              hhr_errcumu = sum(hhr_errcumu, na.rm = TRUE),
                              perc_errcumu = 0) %>%
  mutate(perc_err = round(hhr_err_ct/interviewed*100, 0),
         perc_errcumu = round(hhr_errcumu/interviewed_cumu*100, 0))

# Add totals to tibble
t_5 <- rbind(t_5, t_5tot)

# Create a flextable object
t_5 %>% mutate(spacer = "") %>% # add a spacer for flextable
  select(region, interviewed, hhr_err_ct, perc_err, spacer, interviewed_cumu, hhr_errcumu, perc_errcumu) %>%
  flextable() %>%
# Set headers
  set_header_labels(region = "Region",
                    interviewed = "HHs with data",
                    hhr_err_ct = "Number of HHs",
                    perc_err = "Percentage of HH",
                    spacer = "",
                    interviewed_cumu = "HHs with data",
                    hhr_errcumu = "Number of HHs",
                    perc_errcumu = "Percentage of HH") %>%
  add_header_row(values = c("", "Incorrect count of eligible persons at HHR", "", "Incorrect count of eligible persons at HHR" ), colwidths = c(1, 3, 1, 3) ) %>%
  add_header_row(values = c("", "Daily results", "", "Cumulative results"), colwidths = c(1, 3, 1, 3) ) %>%
  # Footer
  add_footer_lines(paste("Lot definition: district\n",
                         "Source of data: Assessment recount vs participant recall of HHR\n",
                         "Percentage values are based on unweighted counts")) %>%
  # Formatting
  colformat_num(j = "perc_err", suffix = "%") %>%
  colformat_num(j = "perc_errcumu", suffix = "%") %>%
  align(j = "region", align = "left", part = "body") %>%
  align(i = 2, j = NULL, align = "left", part = "header") %>%
  align(i = 3, j = NULL, align = "left", part = "header") %>%
  my_theme() %>%
  # Shade the spacer column as the visual break 
  bg(j = "spacer", bg = "#E6E6E6", part = "all") %>%
  width(j = "spacer", width = 0.1) %>%
  # Set header
  set_caption(caption = paste("Table 5. Percentage of households with HHR errors by region, daily and cumulative total: ",
                              paste("Assessment day ", day)), 
              style = "Table Caption", 
              autonum = run_autonum(seq_id = "tab", bkm = "t_5")) 
```

## Reasons for HHR errors
The following bar chart shows the distribution of reasons for HHR errors by region. This is cumulative for all errors up to day `r day`.

```{r fig2, fig.width = 8}

#- Add bar graph of reasons for mismatch 
# Create a table with the necessary format to plot
fig2 <- hh %>% filter(interviewed == 1 & hhr_err == 1) %>%
  select(region, novisit, reason_mismatch) %>%
  mutate(reason = case_when(novisit == 1 ~ "HH not registered",
                            reason_mismatch == 1 ~ "HHR counted ineligible person(s) as eligible",
                            reason_mismatch == 2 ~ "HHR counted eligible person(s) as ineligible",
                            reason_mismatch == 3 ~ "HHR did not follow HH definition",
                            reason_mismatch == 4 ~ "Household likely inflated number of eligible persons",
                            reason_mismatch == 5 ~ "Reason unknown",
                            reason_mismatch == 96 ~ "Other reason"),
         reason = factor(reason, levels = c("HH not registered", "HHR counted ineligible person(s) as eligible", "HHR counted eligible person(s) as ineligible", "HHR did not follow HH definition", "Household likely inflated number of eligible persons", "Reason unknown", "Other reason"))) %>%
  tabyl(region, reason) %>%
  pivot_longer(cols = -region, names_to = "reason", values_to = "count") %>%
  group_by(region) %>%
  mutate(percent = round(count / sum(count) * 100, 1)) %>%
  ungroup()

# Plot reasons for errors  
fig2 %>% 
  ggplot(aes(x = region, y = percent, fill = reason)) +
  geom_bar(stat = "identity") +
  labs(title = "Reasons for household errors", x = "Region", y = "Percent", fill = "Reasons for HHR errors") +
  theme_minimal()

```

The following two tables provide the number and percentage of households with each type of household error by district (lot) within each region. Table 7a presents results for day `r day` and Table 7b presents cumulative results for days 1 to `r day`. 

Daily results:

```{r t7daily}
# Reason for errors by district, daily 

# Count up number of HHs interviewed by region
t_7a <- hh %>% filter(interviewed == 1 & survey_day == day) %>%
  select(region, district) %>%
  group_by(region, district) %>%   
  summarise(n = n())
# Count up the reasons for mismatches
t_7b <- hh %>% filter(interviewed == 1 & survey_day == day & hhr_err == 1) %>% 
  select(region, district, reason_mismatch) %>%
  mutate(reasons = case_when(reason_mismatch %in% c("1", "2") ~ "eligibility",
                             reason_mismatch == "3" ~ "definition",
                             reason_mismatch == "4" ~ "inflated",
                             reason_mismatch == "5" ~ "unknown",
                             reason_mismatch == "96" ~ "other"),
         reasons = factor(reasons, levels = c("eligibility", "definition", "inflated", "unknown", "other")),
         value = rep(1, nrow(.))) %>% 
  group_by(region, district, reasons) %>%
  summarise(n = n()) %>%
  select(region, district, reasons, n) %>%
  complete(reasons) %>%
  pivot_wider(names_from = reasons, values_from = n)

# Combine the number interviewed with the number of errors
t_7 <- left_join(t_7a, t_7b, by = c("region", "district"))
# Replace NA with zeros
t_7 <- t_7 %>%
  replace(is.na(.), 0) %>%
  rename(interviewed = n) %>%
  mutate(region = as.character(region),
         district = as.character(district),
         toterr = eligibility + definition + inflated + unknown, other,
         elig_p = round(eligibility/interviewed * 100, 0),
         def_p = round(definition/interviewed * 100, 0),
         infl_p = round(inflated/interviewed * 100, 0),
         unk_p = round(unknown/interviewed * 100, 0),
         oth_p = round(other/interviewed * 100, 0),
         tot_p = round(toterr/interviewed * 100, 0)) %>%
  select(region, district, interviewed, eligibility, elig_p, definition, def_p, inflated, infl_p, unknown, unk_p, other, oth_p, toterr, tot_p)

# Create a totals row
t_7tot <- t_7 %>% ungroup() %>% 
  summarise(region = "",
            district = "Total",
            interviewed = sum(interviewed, na.rm = TRUE),
            eligibility = sum(eligibility, na.rm = TRUE),
            elig_p = 0,
            definition = sum(definition, na.rm = TRUE),
            def_p = 0,
            inflated = sum(inflated, na.rm = TRUE),
            infl_p = 0,
            unknown = sum(unknown, na.rm = TRUE),
            unk_p = 0,
            other = sum(other, na.rm = TRUE),
            oth_p = 0,
            toterr = sum(toterr, na.rm = TRUE),
            tot_p = 0) %>%
  mutate(elig_p = round(eligibility/interviewed*100, 0),
         def_p = round(definition/interviewed*100, 0),
         infl_p = round(inflated/interviewed*100, 0),
         unk_p = round(unknown/interviewed*100, 0),
         oth_p = round(other/interviewed*100, 0),
         tot_p = round(toterr/interviewed*100, 0))

# Add totals to tibble
t_7 <- rbind(t_7, t_7tot)

# Create flextable
t_7 %>%
  flextable() %>%
# Create grouping by region
  merge_v(j = "region") %>%
  valign(j = "region", valign = "top") %>%
  bg(i = ~ region == 1, bg = "#f2f2f2", part = "body") %>% # This colors the rows by region 
  bg(i = ~ region == 2, bg = "#e6f7ff", part = "body") %>%
  bg(i = ~ region == 3, bg = "#fff2e6", part = "body") %>%
# Set headers
  set_header_labels(region = "Region",
                    district = "District",
                    interviewed = "HHs with data",
                    eligibility = "No.",
                    elig_p = "%",
                    definition = "No.",
                    def_p = "%",
                    inflated = "No.",
                    infl_p = "%",
                    unknown = "No.",
                    unk_p = "%",
                    other = "No.",
                    oth_p = "%",
                    toterr = "No.",
                    tot_p = "%") %>%
  add_header_row(values = c("", "", "",
                            "HHR miscounted based on eligibility", 
                            "HHR did not follow HH definition", 
                            "HH inflated size", 
                            "HHR miscount, unknown reason", 
                            "Other reason(s)", 
                            "Total errors"), colwidths = c(1, 1, 1, 2, 2, 2, 2, 2, 2)) %>%
  merge_v(j = c("region", "district", "interviewed"), part = "header") %>%
  align(part = "header", align = "center") %>%
  add_header_row(values = c("", "", "", "Incorrect count of eligible persons at HHR"), colwidths = c(1, 1, 1, 12)) %>%
 # Footer
  add_footer_lines(paste("Lot definition: district\n",
                         "Source of data: Assessment recount vs participant recall of HHR\n",
                         "Percentage values are based on unweighted counts")) %>%
  # Formatting
  colformat_num(j = c("elig_p", "def_p", "infl_p","unk_p", "oth_p", "tot_p"), suffix = "%", digit = 1) %>%
  align(i = 2, j = NULL, align = "left", part = "header") %>%
  align(i = 3, j = NULL, align = "left", part = "header") %>%
  my_theme() %>%
  # Set header
set_caption(caption = paste("Table 7a. Distribution of HHR error reasons by district for a given region, daily: ",
                            paste("Assessment day ", day)),
            style = "Table Caption",
            autonum = run_autonum(seq_id = "tab", bkm = "t_a8a"))

```

Cumulative results:

```{r t7cumul}
# Reason for errors by district, cumulative

# Count up number of HHs interviewed by region
t_7a <- hh %>% filter(interviewed == 1) %>%
  select(region, district) %>%
  group_by(region, district) %>%   
  summarise(n = n())
# Count up the reasons for mismatches
t_7b <- hh %>% filter(interviewed == 1 & hhr_err == 1) %>% 
  select(region, district, reason_mismatch) %>%
  mutate(reasons = case_when(reason_mismatch %in% c("1", "2") ~ "eligibility",
                             reason_mismatch == "3" ~ "definition",
                             reason_mismatch == "4" ~ "inflated",
                             reason_mismatch == "5" ~ "unknown",
                             reason_mismatch == "96" ~ "other"),
         reasons = factor(reasons, levels = c("eligibility", "definition", "inflated", "unknown", "other")),
         value = rep(1, nrow(.))) %>% 
  group_by(region, district, reasons) %>%
  summarise(n = n()) %>%
  select(region, district, reasons, n) %>%
  complete(reasons) %>%
  pivot_wider(names_from = reasons, values_from = n)

# Combine the number interviewed with the number of errors
t_7 <- left_join(t_7a, t_7b, by = c("region", "district"))
# Replace NA with zeros
t_7 <- t_7 %>%
  replace(is.na(.), 0) %>%
  rename(interviewed = n) %>%
  mutate(region = as.character(region),
         district = as.character(district),
         toterr = eligibility + definition + inflated + unknown, other,
         elig_p = round(eligibility/interviewed * 100, 0),
         def_p = round(definition/interviewed * 100, 0),
         infl_p = round(inflated/interviewed * 100, 0),
         unk_p = round(unknown/interviewed * 100, 0),
         oth_p = round(other/interviewed * 100, 0),
         tot_p = round(toterr/interviewed * 100, 0)) %>%
  select(region, district, interviewed, eligibility, elig_p, definition, def_p, inflated, infl_p, unknown, unk_p, other, oth_p, toterr, tot_p)

# Create a totals row
t_7tot <- t_7 %>% ungroup() %>% 
  summarise(region = "",
            district = "Total",
            interviewed = sum(interviewed, na.rm = TRUE),
            eligibility = sum(eligibility, na.rm = TRUE),
            elig_p = 0,
            definition = sum(definition, na.rm = TRUE),
            def_p = 0,
            inflated = sum(inflated, na.rm = TRUE),
            infl_p = 0,
            unknown = sum(unknown, na.rm = TRUE),
            unk_p = 0,
            other = sum(other, na.rm = TRUE),
            oth_p = 0,
            toterr = sum(toterr, na.rm = TRUE),
            tot_p = 0) %>%
  mutate(elig_p = round(eligibility/interviewed*100, 0),
         def_p = round(definition/interviewed*100, 0),
         infl_p = round(inflated/interviewed*100, 0),
         unk_p = round(unknown/interviewed*100, 0),
         oth_p = round(other/interviewed*100, 0),
         tot_p = round(toterr/interviewed*100, 0))

# Add totals to tibble
t_7 <- rbind(t_7, t_7tot)

# Create flextable
t_7 %>%
  flextable() %>%
# Create grouping by region
  merge_v(j = "region") %>%
  valign(j = "region", valign = "top") %>%
  bg(i = ~ region == 1, bg = "#f2f2f2", part = "body") %>% # This colors the rows by region 
  bg(i = ~ region == 2, bg = "#e6f7ff", part = "body") %>%
  bg(i = ~ region == 3, bg = "#fff2e6", part = "body") %>%
# Set headers
  set_header_labels(region = "Region",
                    district = "District",
                    interviewed = "HHs with data",
                    eligibility = "No.",
                    elig_p = "%",
                    definition = "No.",
                    def_p = "%",
                    inflated = "No.",
                    infl_p = "%",
                    unknown = "No.",
                    unk_p = "%",
                    other = "No.",
                    oth_p = "%",
                    toterr = "No.",
                    tot_p = "%") %>%
  add_header_row(values = c("", "", "",
                            "HHR miscounted based on eligibility", 
                            "HHR did not follow HH definition", 
                            "HH inflated size", 
                            "HHR miscount, unknown reason", 
                            "Other reason(s)", 
                            "Total errors"), colwidths = c(1, 1, 1, 2, 2, 2, 2, 2, 2)) %>%
  merge_v(j = c("region", "district", "interviewed"), part = "header") %>%
  align(part = "header", align = "center") %>%
  add_header_row(values = c("", "", "", "Incorrect count of eligible persons at HHR"), colwidths = c(1, 1, 1, 12)) %>%
 # Footer
  add_footer_lines(paste("Lot definition: district\n",
                         "Source of data: Assessment recount vs participant recall of HHR\n",
                         "Percentage values are based on unweighted counts")) %>%
  # Formatting
  colformat_num(j = c("elig_p", "def_p", "infl_p","unk_p", "oth_p", "tot_p"), suffix = "%", digit = 1) %>%
  align(i = 2, j = NULL, align = "left", part = "header") %>%
  align(i = 3, j = NULL, align = "left", part = "header") %>%
  my_theme() %>%
  # Set header
set_caption(caption = paste("Table 7b. Distribution of HHR error reasons by district for a given region, cumulative: ",
                            paste("Assessment day ", day)),
            style = "Table Caption",
            autonum = run_autonum(seq_id = "tab", bkm = "t_7b"))

```

The following tables (Table 8a and 8b) present the same data as Tables 7a and 7b (HHR errors) but summarized by region rather than district (lot). Table 8a presents results for day `r day` and Table 8b presents cumulative results.

Daily results:

```{r t8daily}

# Reason for errors by region (daily)

# Count up number of HHs interviewed by region
t_8a <- hh %>% filter(interviewed == 1 & survey_day == day) %>%
  select(region) %>%
  group_by(region) %>%   
  summarise(n = n())
# Count up the reasons for mismatches
t_8b <- hh %>% filter(interviewed == 1 & survey_day == day & hhr_err_ct == 1) %>% 
  select(region, reason_mismatch) %>%
  mutate(reasons = case_when(reason_mismatch %in% c("1", "2") ~ "eligibility",
                             reason_mismatch == "3" ~ "definition",
                             reason_mismatch == "4" ~ "inflated",
                             reason_mismatch == "5" ~ "unknown",
                             reason_mismatch == "96" ~ "other"),
         reasons = factor(reasons, levels = c("eligibility", "definition", "inflated", "unknown", "other")),
         value = rep(1, nrow(.))) %>% 
  group_by(region, reasons) %>%
  summarise(n = n()) %>%
  select(region, reasons, n) %>%
  complete(reasons) %>%
  pivot_wider(names_from = reasons, values_from = n)

# Combine the number interviewed with the number of errors
t_8 <- left_join(t_8a, t_8b, by = "region")
# Replace NA with zeros
t_8 <- t_8 %>%
  replace(is.na(.), 0) %>%
  rename(interviewed = n) %>%
  mutate(toterr = eligibility + definition + inflated + unknown, other,
         elig_p = round(eligibility/interviewed * 100, 0),
         def_p = round(definition/interviewed * 100, 0),
         infl_p = round(inflated/interviewed * 100, 0),
         unk_p = round(unknown/interviewed * 100, 0),
         oth_p = round(other/interviewed * 100, 0),
         tot_p = round(toterr/interviewed * 100, 0)) %>%
  select(region, interviewed, eligibility, elig_p, definition, def_p, inflated, infl_p, unknown, unk_p, other, oth_p, toterr, tot_p)

# Create a totals row
t_8tot <- t_8 %>% summarise(region = "Total",
                              interviewed = sum(interviewed, na.rm = TRUE),
                              eligibility = sum(eligibility, na.rm = TRUE),
                              elig_p = 0,
                              definition = sum(definition, na.rm = TRUE),
                              def_p = 0,
                              inflated = sum(inflated, na.rm = TRUE),
                              infl_p = 0,
                              unknown = sum(unknown, na.rm = TRUE),
                              unk_p = 0,
                              other = sum(other, na.rm = TRUE),
                              oth_p = 0,
                              toterr = sum(toterr, na.rm = TRUE),
                              tot_p = 0) %>%
  mutate(elig_p = round(eligibility/interviewed*100, 0),
         def_p = round(definition/interviewed*100, 0),
         infl_p = round(inflated/interviewed*100, 0),
         unk_p = round(unknown/interviewed*100, 0),
         oth_p = round(other/interviewed*100, 0),
         tot_p = round(toterr/interviewed*100, 0))

# Add totals to tibble
t_8 <- rbind(t_8, t_8tot)

# Create flextable
t_8 %>%
  flextable() %>%
# Set headers
  set_header_labels(region = "Region",
                    interviewed = "HHs with data",
                    eligibility = "No.",
                    elig_p = "%",
                    definition = "No.",
                    def_p = "%",
                    inflated = "No.",
                    infl_p = "%",
                    unknown = "No.",
                    unk_p = "%",
                    other = "No.",
                    oth_p = "%",
                    toterr = "No.",
                    tot_p = "%") %>%
  add_header_row(values = c("", "",
                            "HHR miscounted based on eligibility", 
                            "HHR did not follow HH definition", 
                            "HH inflated size", 
                            "HHR miscount, unknown reason", 
                            "Other reason(s)", 
                            "Total errors"), colwidths = c(1, 1, 2, 2, 2, 2, 2, 2)) %>%
  merge_v(j = c("region", "interviewed"), part = "header") %>%
  align(part = "header", align = "center") %>%
  add_header_row(values = c("", "", "Incorrect count of eligible persons at HHR"), colwidths = c(1, 1, 12)) %>%
 # Footer
  add_footer_lines(paste("Lot definition: district\n",
                         "Source of data: Assessment recount vs participant recall of HHR\n",
                         "Percentage values are based on unweighted counts")) %>%
  # Formatting
  colformat_num(j = c("elig_p", "def_p", "infl_p","unk_p", "oth_p", "tot_p"), suffix = "%", digit = 1) %>%
  align(i = 2, j = NULL, align = "left", part = "header") %>%
  align(i = 3, j = NULL, align = "left", part = "header") %>%
  my_theme() %>%
  # Set header
set_caption(caption = paste("Table 8a. Distribution of HHR error reasons by region, daily: ",
                            paste("Assessment day ", day)),
            style = "Table Caption")

```

Cumulative results:

```{r t8cumul}

# Count up number of HHs interviewed by region
t_8a <- hh %>% filter(interviewed == 1) %>%
  select(region) %>%
  group_by(region) %>%   
  summarise(n = n())
# Count up the reasons for mismatches
t_8b <- hh %>% filter(interviewed == 1 & hhr_err_ct == 1) %>%
  select(region, reason_mismatch) %>%
  mutate(reasons = case_when(reason_mismatch %in% c("1", "2") ~ "eligibility",
                             reason_mismatch == "3" ~ "definition",
                             reason_mismatch == "4" ~ "inflated",
                             reason_mismatch == "5" ~ "unknown",
                             reason_mismatch == "96" ~ "other"),
         reasons = factor(reasons,
                          levels = c("eligibility", "definition", "inflated", "unknown", "other")),
         value = rep(1, nrow(.))) %>% 
  group_by(region, reasons) %>%
  summarise(n = n()) %>%
  select(region, reasons, n) %>%
  complete(reasons) %>%
  pivot_wider(names_from = reasons, values_from = n)

# Combine the number interviewed with the number of errors
t_8 <- left_join(t_8a, t_8b, by = "region")
# Replace NA with zeros
t_8 <- t_8 %>%
  replace(is.na(.), 0) %>%
  rename(interviewed = n) %>%
  mutate(toterr = eligibility + definition + inflated + unknown, other,
         elig_p = round(eligibility/interviewed * 100, 0),
         def_p = round(definition/interviewed * 100, 0),
         infl_p = round(inflated/interviewed * 100, 0),
         unk_p = round(unknown/interviewed * 100, 0),
         oth_p = round(other/interviewed * 100, 0),
         tot_p = round(toterr/interviewed * 100, 0)) %>%
  select(region, interviewed, eligibility, elig_p, definition, def_p, inflated, infl_p, unknown, unk_p, other, oth_p, toterr, tot_p)

# Create a totals row
t_8tot <- t_8 %>% summarise(region = "Total",
                              interviewed = sum(interviewed, na.rm = TRUE),
                              eligibility = sum(eligibility, na.rm = TRUE),
                              elig_p = 0,
                              definition = sum(definition, na.rm = TRUE),
                              def_p = 0,
                              inflated = sum(inflated, na.rm = TRUE),
                              infl_p = 0,
                              unknown = sum(unknown, na.rm = TRUE),
                              unk_p = 0,
                              other = sum(other, na.rm = TRUE),
                              oth_p = 0,
                              toterr = sum(toterr, na.rm = TRUE),
                              tot_p = 0) %>%
  mutate(elig_p = round(eligibility/interviewed*100, 0),
         def_p = round(definition/interviewed*100, 0),
         infl_p = round(inflated/interviewed*100, 0),
         unk_p = round(unknown/interviewed*100, 0),
         oth_p = round(other/interviewed*100, 0),
         tot_p = round(toterr/interviewed*100, 0))

# Add totals to tibble
t_8 <- rbind(t_8, t_8tot)

# Create flextable
t_8 %>%
  flextable() %>%
# Set headers
  set_header_labels(region = "Region",
                    interviewed = "HHs with data",
                    eligibility = "No.",
                    elig_p = "%",
                    definition = "No.",
                    def_p = "%",
                    inflated = "No.",
                    infl_p = "%",
                    unknown = "No.",
                    unk_p = "%",
                    other = "No.",
                    oth_p = "%",
                    toterr = "No.",
                    tot_p = "%") %>%
  add_header_row(values = c("", "",
                            "HHR miscounted based on eligibility", 
                            "HHR did not follow HH definition", 
                            "HH inflated size", 
                            "HHR miscount, unknown reason", 
                            "Other reason(s)", 
                            "Total errors"), colwidths = c(1, 1, 2, 2, 2, 2, 2, 2)) %>%
  merge_v(j = c("region", "interviewed"), part = "header") %>%
  align(part = "header", align = "center") %>%
  add_header_row(values = c("", "", "Incorrect count of eligible persons at HHR"), colwidths = c(1, 1, 12)) %>%
 # Footer
  add_footer_lines(paste("Lot definition: district\n",
                         "Source of data: Assessment recount vs participant recall of HHR\n",
                         "Percentage values are based on unweighted counts")) %>%
  # Formatting
  colformat_num(j = c("elig_p", "def_p", "infl_p","unk_p", "oth_p", "tot_p"), suffix = "%", digit = 1) %>%
  align(i = 2, j = NULL, align = "left", part = "header") %>%
  align(i = 3, j = NULL, align = "left", part = "header") %>%
  my_theme() %>%
  # Set caption
  set_caption(caption = "Table 8b. Distribution of HHR error reasons by region, cumulative", 
              style = "Table Caption") 

```

# Summary

This section provides a summary of assessment outcomes and reasons for errors, as well as the lot classification. These are meant to be generated at the end of data collection and should be ignored or excluded until the final day of data collection.  

Table 9 summarizes the number and direction (over- or undercounting of eligible persons) for HHR errors.

```{r table9}

# Summary of number of matches (no errors) and mismatches (errors) in HHR
t_9 <- hh %>% 
  summarise(across(c(interviewed, calc_elig_correct, hhr_hi, hhr_lo), \(x) sum(x, na.rm = TRUE)), .groups = "drop") %>%
  mutate(match_p = round(calc_elig_correct/interviewed * 100, 0), # !!! Using all HH interviewed which means that percentages won't add up to zero (as some HHs were missed and don't have a count). Alternatively could used "visited" here
         hi_p = round(hhr_hi/interviewed * 100, 0),
         lo_p = round(hhr_lo/interviewed * 100, 0),
         ds = "Assessment recount vs participant recall of HHR") %>%
  select(ds, interviewed, calc_elig_correct, match_p, calc_elig_correct, hhr_hi, hi_p, hhr_lo, lo_p)

# Create flextable object
t_9 %>%
  flextable() %>%
# Set headers
  set_header_labels(ds = "Data source",
                    interviewed = "HHs with data", 
                    calc_elig_correct = "No.",
                    match_p = "%",
                    hhr_hi = "No.",
                    hi_p = "%",
                    hhr_lo = "No.",
                    lo_p = "%") %>%
  add_header_row(values = c("", "", 
                            "Matches\nCorrect count of eligible persons at HHR",
                            "HHR higher than assessment",
                            "HHR lower than assessment"),
                 colwidth = c(1, 1, 2, 2, 2)) %>%
  merge_v(j = c("ds", "interviewed"), part = "header") %>%
  align(part = "header", align = "center") %>%
  add_header_row(values = c("", "", "", "Mismatches\nIncorrect count of eligible persons at HHR"), 
                 colwidths = c(1, 1, 2, 4)) %>%
  merge_v(j = c("ds", "interviewed", "calc_elig_correct", "match_p"), part = "header") %>%
  align(part = "header", align = "center") %>%
 # Footer
  add_footer_lines(paste("Lot definition: district\n",
                         "Percentage values are based on unweighted counts")) %>%
  # Formatting
  colformat_num(j = c("match_p", "hi_p", "lo_p"), suffix = "%", digit = 1) %>%
  align(i = 2, j = NULL, align = "center", part = "header") %>%
  align(i = 3, j = NULL, align = "center", part = "header") %>%
  my_theme() %>%
  # Set header
  set_caption(caption = paste("Table 9. Campaign assessment summary of total HHR errors and direction of error"),
              style = "Table Caption") 

```

Table 10 provides a summary of the reasons for errors in HHR in households that reported a visit from the HHR team.

```{r table10, echo = FALSE}

# Create a table with total interviewed, numbers of HHs with errors, and percentages
totals <- hh %>% 
  summarise(across(c(interviewed, calc_elig_correct, hhr_err_ct), \(x) sum(x, na.rm = TRUE)), .groups = "drop") 

# Create an object with the total number interviewed and the total number of HHs with errors
interviewed_total <- totals$interviewed
hhr_err_total <- totals$hhr_err_ct

# Pivot totals into a vertical table and create some additional columns for totals and percentages
t_10a <- totals %>% 
  pivot_longer(everything(),
               names_to  = "variable",
               values_to = "n") %>% 
   mutate(perc_tot = case_when(variable != "interviewed" ~ round(n/interviewed_total*100, 1)),
         percent = NA)
  
# Create table section with the reasons for higher HHR count
t_10b <- hh %>% filter(hhr_hi == 1) %>%
  mutate(reasons = case_when(reason_mismatch == "1" ~ "h_eligibility",
                             reason_mismatch == "3" ~ "h_definition",
                             reason_mismatch == "4" ~ "h_inflated",
                             reason_mismatch == "5" ~ "h_unknown",
                             reason_mismatch == "96" ~ "h_other"),
         reasons = factor(reasons, levels = c("h_eligibility", "h_definition", "h_inflated", "h_unknown", "h_other"))) %>%
  tabyl(reasons) %>% 
  adorn_totals("row")
# Tidy up percentages and add a column of percentage of totals (to be filled in after)
t_10b <- as_tibble(t_10b) %>% 
  mutate(percent = case_when(reasons != "Total" ~ round(percent*100, 0),
                             reasons == "Total" ~ round(n/hhr_err_total*100, 0)),
         perc_tot = round(n/interviewed_total*100, 0),
         reasons = case_when(reasons == "Total" ~ "h_total",
                             TRUE ~ as.character(reasons))) %>%
  rename(variable = reasons) %>%
  select(variable, n, perc_tot, percent) %>%
  arrange(factor(variable, levels = c("h_total", "h_eligibility", "h_definition", "h_inflated", "h_unknown", "h_other")))
  
# Create table section with the reasons for lower HHR count
t_10c <- hh %>% filter(hhr_lo == 1) %>%
  mutate(reasons = case_when(reason_mismatch == "2" ~ "l_eligibility",
                             reason_mismatch == "3" ~ "l_definition", # !!! This isn't included in the dummy table but there are some examples in dummy data
                             reason_mismatch == "5" ~ "l_unknown",
                             reason_mismatch == "96" ~ "l_other"),
         reasons = factor(reasons, levels = c("l_eligibility", "l_definition", "l_unknown", "l_other"))) %>%
  tabyl(reasons) %>% 
  adorn_totals("row")
# Tidy up percentages and add a column of percentage of totals (to be filled in after)
t_10c <- as_tibble(t_10c) %>% 
  mutate(percent = case_when(reasons != "Total" ~ round(percent*100, 0),
                             reasons == "Total" ~ round(n/hhr_err_total*100, 0)),
         perc_tot = round(n/interviewed_total*100, 0),
         reasons = case_when(reasons == "Total" ~ "l_total",
                             TRUE ~ as.character(reasons))) %>%
  rename(variable = reasons) %>%
  select(variable, n, perc_tot, percent) %>%
  arrange(factor(variable, levels = c("l_total", "l_eligibility", "l_definition", "l_unknown", "l_other")))
  
# Combine everything
t_10 <- bind_rows(t_10a, t_10b, t_10c)
# Rename the row labels
t_10 <- t_10 %>% 
  mutate(variable = case_match(variable, "interviewed" ~ "Total households assessed",
                               "calc_elig_correct" ~ "Households with matched HHR and assessment results\nCorrect count of eligible persons at HHR",
                               "hhr_err" ~ "Households with unmatched HHR and assessment results\nIncorrect count of eligible persons at HHR", 
                               "h_total" ~ "Higher HHR count than assessment recount",
                               "h_eligibility" ~ "HHR counted ineligible person(s) as eligible",
                               "h_definition" ~ "HHR definition did follow HH definition",
                               "h_inflated" ~ "Household likely inflated number of eligible persons",
                               "h_unknown" ~ "HHR miscount, unknown reason",
                               "h_other" ~ "Other reason",
                               "l_total" ~ "Lower HHR count than assessment recount",
                               "l_eligibility" ~ "HHR counted eligible person(s) as ineligible",
                               "l_definition" ~ "HHR definition did follow HH definition",
                               "l_unknown" ~ "HHR miscount, unknown reason",
                               "l_other" ~ "Other reason")) 

# Create flextable object
t_10 %>%
  flextable() %>%
# Set headers
  set_header_labels(variable = "",
                    n = "No.",
                    perc_tot = "% of total",
                    percent = "% of subgroup") %>%
  # Footer
  add_footer_lines(paste("Lot definition: district\n",
                         "Source of data: Allocation rule applied to assessment recount vs participant recall of number of ITNs received\n",
                         "Percentage values are based on unweighted counts")) %>%
  # Formatting
  colformat_num(j = c("perc_tot", "percent"), suffix = "%", digit = 1) %>%
  bg(i = c(1, 4, 10), bg =  "#D9EAF7") %>%
  my_theme() %>%
  # Set caption
  set_caption(caption = "Table 10. Campaign summary of assessment outcomes and categorized reasons for errors", 
              style = "Table Caption") 

```

Table 11 provides the lot classification. As a reminder, this should only be run at the end of data collection when the data are complete to classify lots based on the full dataset.

```{r lotclass, echo = FALSE}
# Lot classification
lotc <- hh %>% group_by(region, district) %>%
  summarise(across(c(interviewed, hhr_err), \(x) sum(x, na.rm = TRUE)), .groups = "drop") %>%
  mutate(classification = case_when(between(hhr_err, 0, 3) ~ "Good",
                                    between(hhr_err, 4, 8) ~ "Uncertain",
                                    hhr_err > 8 ~ "Inadequate")) %>% 
  select(region, district, hhr_err, classification) %>%
  arrange(region, district) 

# Create a flextable object 
lotc %>%
  flextable() %>%
  merge_v(j = "region") %>%
  valign(j = "region", valign = "top") %>%
  set_header_labels(region = "Region",
                    district = "District (lot)",
                    hhr_err = "Number of HHs with incorrect HHR count",
                    classification = "Classification") %>%
  set_caption(caption = "Table 11. Classification of lots based on correct count of eligible persons during HHR.", 
              style = "Table Caption") %>% 
  # Color in cells based on classification
  bg(i = ~ classification == "Good", j = "classification", bg = "#d9ead3") %>%
  bg(i = ~ classification == "Uncertain", j = "classification", bg = "#fff2cc") %>%     
  bg(i = ~ classification == "Inadequate", j = "classification", bg = "#f4cccc") %>%
  # Footer text
  add_footer_lines(paste("Data source:\n",
                         "Assessment recount vs participant recall of HHR",
                       sep = "")) %>%
  add_footer_lines(paste("Decision rules (assuming 60 HH denominator):\n",
                         "0-3 failures = Good\n",
                         "4-8 failures = Uncertain\n",
                         "9+ failures = Inadequate",
                       sep = "")) %>%
  my_theme()

```





